title

### 2016-05-13 paper.tex
paper: fix build
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

\usepackage[unicode=true]{hyperref}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            citecolor=blue
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

\begin{figure}[h]
  \centering
    \includegraphics[width=0.45\textwidth]{experiments/objclass-dev/output.png}
    \caption{
[\href{https://github.com/noahdesu/zlog-popper/tree/master/experiments/objclass-dev/visualize.ipynb}{source}]
Growth of officially supported, custom object interfaces in RADOS over 6
years. A \emph{method} is a specific object interface and a \emph{class} is a
logical grouping of methods.
}
\end{figure}

@@

>>>>

\usepackage[unicode=true]{hyperref}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

Cloud providers are increasingly reliant upon extensions to distributed
storage system such as Ceph as is shown in Figure~\ref{fig:objclass-dev}
by a marked increase in production Ceph extensions. The construction of
extensions is not limited to core developers; the community has been receptive
to contributions with the recent inclusion by CERN developers of an extension
for performing limited numeric operations on object data~\cite{cls_numops}.

\begin{figure}[h]
  \centering
    \includegraphics[width=0.45\textwidth]{experiments/objclass-dev/output.png}
    \caption{
[\href{https://github.com/noahdesu/zlog-popper/tree/master/experiments/objclass-dev/visualize.ipynb}{source}]
Growth of officially supported, custom object interfaces in RADOS over 6
years. A \emph{method} is a specific object interface and a \emph{class} is a
logical grouping of methods.
}
\label{fig:objclass-dev}
\end{figure}

@@

\bibliography{paper}
\bibliographystyle{plain}
